---
title: "Data Cleansing & Formatting"
output: html_notebook
author: Syifa Humaira
---

# Load Library
```{r}
library(readxl)
library(lubridate)
library(DataExplorer)
library(dplyr)
```

#Import data excel
```{r}
Online_Retail <- read_excel("E:/Data MBA IYKRA/Online-Retail.xlsx")
```

#Check missing data
```{r}
plot_missing(Online_Retail)
```

#Summary of the data
```{r}
summary(Online_Retail)
```

#Preview of the first 6 rows and last 6 rows of data
```{r}
head(Online_Retail)
tail(Online_Retail)
```

#Check Varible data
```{r}
str(Online_Retail)
```

#Visualize Data Structure
```{r}
plot_str(Online_Retail)
```

#Drop missing the value in CustomerID
```{r}
Online_Retail_drop <- Online_Retail [!is.na(Online_Retail$CustomerID),]
```

#View Data after Drop the missing the value
```{r}
View(Online_Retail_drop)
```

#Summary of Data after Drop missing the value
```{r}
summary(Online_Retail_drop)
```

#Check missing Data after Drop missing the value
```{r}
plot_missing(Online_Retail_drop)
```

#Visualize bar graph of the Country
```{r}
plot_bar(Online_Retail_drop$Country)
```

#Change the name of Country using gsub
```{r}
Online_Retail_drop$Country <- gsub('United Kingdom', 'Inggris', Online_Retail_drop$Country)
```

#Checkin the Country after change the name with visualize bar graph
```{r}
plot_bar(Online_Retail_drop)
```

#Now we're going to make a new table :
# CustomerID | Recency | Frequency | Monetary
# Recency   : Days count from 2011-12-31 to the last transaction made (in days)
# Frequency : Transaction count in the last 6 months
# Monetary  : Money spent for transaction by distinct CustomerID (in dollars)

```{r}
frequency <- Online_Retail_drop %>% group_by(CustomerID) %>% summarise(frequency = n_distinct(InvoiceNo))
```

```{r}
monetary <- Online_Retail_drop %>% group_by(CustomerID) %>% summarise(monetary=sum(UnitPrice*Quantity))
```

```{r}
recency <- Online_Retail_drop %>% group_by(CustomerID) %>% arrange(desc(InvoiceDate)) %>%   filter(row_number()==1) %>% mutate(recency = as.numeric(as.duration(interval(InvoiceDate,ymd("2011-12-31"))))/86400) %>% select(CustomerID, recency)
```

# Make the new table by joining the 3 new variable
```{r}
df_rfm <- recency %>% left_join(frequency,by="CustomerID") %>% left_join(monetary,by="CustomerID")
```

#Summaries data RFM
```{r}
summary(df_rfm)

```

# Make a csv file from the table
```{r}
write.csv(df_rfm,"Online_Retail_RFM.csv")
```

